\newpage
\TOCadd{Acknowledgements}

\begin{center}
ACKNOWLEDGEMENTS
\end{center}

\noindent I would like to thank:
\begin{description}
\item[my parents, Henry Lange and Elisabeth Jahren,]
    for giving me an environment where I can grow up to enjoy learning, and their never ending love and support.
\item[Kayla Mclean and the other graduate students,]
    for keeping me human throughout this journey.
\item[Dr.~Maxim Pospelov,]
    for taking me under his wing, providing an interesting project to work on, and for knowing when to guide me and when to let me explore.
\item[University of Victoria and the Department of Physics and Astronomy,]
    for giving me both the point of view of an undergraduate student, and a graduate student, for providing funding and scholarships, and for an office to call my own.
\item[Perimeter Institute for Theoretical Physics,]
    for providing a place to learn, be productive, and meet new people.
\end{description}

\begin{flushright}
\textit{I can live with doubt, and uncertainty, and not
knowing. I think it's much more interesting to live not
knowing than to have answers which might be wrong.
I have approximate answers, and possible beliefs,
and different degrees of certainty about different things,
but I'm not absolutely sure of anything.
There are many things I don't know anything about,
such as whether it means anything to ask ``Why are we here?"
I might think about it a little bit, and if I can't
figure it out then I go on to something else.
But I don't have to know an answer.
I don't feel frightened by not knowing things,
by being lost in the mysterious universe without having any purpose —
which is the way it really is, as far as I can tell.
Possibly. It doesn't frighten me.}
\\
Richard Feynman\\
\end{flushright}
