\section{$e^+ e^-$ Collisions at B-factories}
\label{sec:ee_experiment}
The B-factories \babar~\cite{Boutigny:1995ib}, \belle~\cite{Cheng:1995im}, and the future experiment \belletwo~\cite{Abe:2010gxa} provide high intensity collisions while still reaching higher energies than typical meson decays have access to.
These experiments are used to produce many $B$ mesons by tuning the energy to the $\Upsilon(4S)$ resonance.
The $\Upsilon(4S)$ is a $b\bar{b}$ quark bound state with a large preference to decay to $B$ mesons, having a branching ratio $> 0.96$ \cite{Agashe:2014kda}.
For an $e^+ e^-$ collider of $3.5~\textrm{GeV}$ and $8~\textrm{GeV}$ respectively, the centre-of-mass energy is $\sim 2\sqrt{E_+ E_-} = 10.58~\textrm{GeV}$; at this energy the $\Upsilon(4S)$ is just barely produced and must be at rest in the centre-of-mass frame.
The \kekb collider provides high and low energy rings of electrons and positrons, called the HER and the LER, for the \belle experiment.
SLAC provides the collider for the \babar detector.
It is important to note that the beam energies are asymmetric.
This is to give any decay products a boost down the beam pipe before decaying, extending their lifetimes in the lab frame due to Lorentz time dilation.
It also allows one to more clearly measure the vertex displacement from the production of the $\Upsilon$ to its decay point.
To this end, the detector is also built with this forward direction in mind.
This energy just happens to be right above the threshold for a decay into a pair of $B$ mesons, which have interesting properties to study. For instance, one can measure the amount of CP violation present in the $B/\bar{B}$ system.
It is also possible to measure the neutral $B$ meson oscillation into its anti-particle, $\bar{B^0} \leftrightarrow B^0$.
Measuring CP violation was the primary mission of the \babar experiment.
Over their lifetimes, when \belle ran from 1999-2010, \belle collected $\sim 1000~\textrm{fb}^{-1}$ worth of data, and \babar collected roughly half of this.
The new experiment, \belletwo, will be operating in conjunction with upgrades to the \kekb collider, where it will be rebranded as the \superkekb collider \cite{Akeroyd:2004mj}.
Commissioning for the new collider and detector upgrades begins in 2016.
It is expected that $100$ times the integrated luminosity in $e^+ e^-$ decays will be collected over its lifetime, reaching $\order(10-100)~\textrm{ab}^{-1}$.
It will operate at the same centre of mass energy, but with less of a trade off to the asymmetry by using a $4~\textrm{GeV}$ positron beam and a $7~\textrm{GeV}$ electron beam.

In this work, these B-factories are interesting because they allow access to mediator masses up to $\sim 10~\textrm{GeV}$.
Our model will couple leptons to a new scalar particle with a strength proportional to the mass of the lepton.
In the other experiments discussed so far, \mueee, NA48/2, and NA62, we were limited to couple to muons.
However, at this scale, tau leptons are copiously produced with enough room in the phase space to still have associated emission of dark scalars.
For our purposes of exploring the sensitivity reach, we will consider these three experiments to be the same, with a difference in the total integrated luminosity.
We do not simulate the detector performance, which will be sufficient for this work.
Another main reason why we target the \babar and \belle experiments in this thesis is that there is already a lot of data taken on tape.
\babar and \belle blind their data during analysis, so unless the analysis is performed, it is not possible to know if there are any events present that correspond to our final state, $\tau^+ \tau^- \phi,~\phi \rightarrow \ell^+ \ell^-$.
Note that this also implies that any limits we place are merely potential limits on the sensitivity, not strict upper limits.
Dedicated experimental analyses will be required to conduct the search of $\phi$ via the signature that we suggest.
